Hierarchical Region-Network Sparsity for\\ High-Dimensional Inference in Brain Imaging

### 2016-12-06 paper/ipmi2017/paper.tex
interm

\begin{abstract}
    Structured sparsity penalization has recently improved
    statistical models applied to high-dimensional data in various domains.
    %
    As an extension to imaging neuroscience,
    the present work incorporates
    priors on network hierarchies of brain regions into
    logistic-regression to distinguish neural activity effects.
    These priors bridge two separately studied levels
    of brain architecture:
    functional segregation into regions and
    functional integration by networks.
    %
    Hierarchical region-network priors are shown to better classify
    and recover 
    18 psychological tasks than other sparse estimators.
    Varying the relative importance of
    region and network structure within the hierarchical tree penalty
    captured complementary aspects of the neural activity patterns.
    %
    Local and global priors of neurobiological knowledge
    are thus demonstrated to enhance
    generalization performance, sample complexity, and domain interpretability.
\end{abstract}

\section{Introduction}
% sparsity
Many quantitative scientific domains underwent a
recent shift from the classical ``long data" regime to
the high-dimensional ``wide data" regime.
% the high-dimensional regime (i.e., ``wide data") \cite{jordan2015massive}.
In the brain imaging domain,
many contemporary technologies for acquiring brain signals yield many
more variables per observation than
total observations per data sample.
This $n \ll p$ scenario challenges various statistical methods from
classical statistics.
For instance,
estimating generalized linear models without additional assumptions
yields an underdetermined system of equations.
%
Many such ill-posed estimation problems
have benefited from
\textit{sparsity} assumptions
\cite{bach2012optimization}.
They act as regularizer by encouraging zero coefficients
in model selection.
Sparse supervised and unsupervised
learning algorithms have proven to yield
statistical relationships that can be readily
estimated, reproduced, and interpreted.
%
Moreover, \textit{structured sparsity} can impose
domain knowledge on the 
statistical estimation,
thus shrinking and selecting variables guided by
expected data distributions
\cite{bach2012optimization}.
These restrictions to model complexity
are an attractive plan of attack
for the $\textgreater$100,000 variables per brain map.
Yet, what neurobiological structure best lends itself
to exploitation using structured sparsity priors?

@@

\section*{Methods}
This paper contributes a domain adaptation of hierarchical structured

@@

to create a set of convex sparse penalty terms.

@@

global connectivity when discriminating defined psychological tasks

@@

this study simultaneously infers

@@

Major brain networks emerge in human individuals around birth
\cite{doria2010}.
Their nodes have more
similar functional profiles than nodes from different networks
\cite{anderson2013}.
As a popular method for network extraction,
ICA \cite{beckmann2005} yields continuous brain maps with
weights for each voxel. The region nodes of ICA
network are spatially disjoint sets of voxel groups that
agree with boundaries of brain atlases.
Hence,
each region from a brain atlas can be uniquely associated with one of
the extracted ICA networks.
%
Here, previously published network definitions
obtained using ICA \cite{smith2009}
and
region definitions obtained from
spatially constrained clustering \cite{crad12}
allowed constructing a hierarchy of global ICA networks with their
assigned local cluster regions
(Figure \ref{fig_priors}).
The ensuing network-region tree was used as a frequentist prior
of expected weight distributions
to advantageously bias supervised model fitting.

Specifically, this tree structure was plugged into
hierarchical sparsity penalty terms
\cite{jenatton2012multi}.
It extends the group lasso
\cite{yuan2006model}
by permitting variable groups that contain each other
in a nested tree structure.
The first hierarchical level are
the network groups with all
the voxels of the brain regions associated with them.
Each network node in turn descends into a second hierarchical level with
brain regions of neighboring voxels.
%
Induced by the region-network sparsity tree,
a child node enters the set of relevant voxel variables only
if its parent node has been selected
\cite{bach2012optimization}.
Conversely,
if a parent node is deselected,
also the voxel variables of all child nodes are deselected.
%
Moreover,
the coefficients of all region or all network groups can
be weighed individually.
Trading off the voxel penalties of the network level against the
voxel penalties of the region level
we can design distinct estimation regimes.
%
% Setting a low penalty on the network groups makes it is probable
% that all of them are active in the estimated weight maps. If we then select
% higher penalties on region groups, selection of relevant region groups is
% forced without obeying network definitions.
% Conversely, setting low penalties on the region definitions
% makes it possible for
% all voxels to be active. Selecting higher penalties on the networks then
% leads to a selection of networks with all regions associated with it.
%
% This region-network equilibrium allows inspecting the relative contributions
% of the region and network levels
% of the hierarchical tree prior.

% \paragraph{Problem formulation.}
\subsection{Problem formulation}
We formulate our estimation problem in the framework of regularized
empirical risk
minimization applied to linear models.
The goal is to estimate a good predictor of psychological tasks
given a single brain image. Let the set \(\mathcal X\in\mathbb{R}^{n \times p}\) represent brain
images of \(p > 0\) voxels.
We then minimize the risk \(\mathcal L(\hat y, y)\) with
\(\hat y = f(X\hat w + \hat b)\), where \(f\) is a link function 
(e.g., sigmoid for logistic regression, identity for linear regression),
and \(\mathcal L\) usually represents an appropriate negative loglikelihood.
We incorporate an informative prior through regularization:
\[\argmin_{w, b} \mathcal L(f(Xw + b), y) + \lambda\Omega(w),\]
where \(\lambda > 0\) and \(\Omega\) is the regularizer.
Brain \textit{regions} are defined as disjoint groups of voxels. Let \(\mathcal G\)
be a partition of \(\{1, \dots, p\}\), i.e.
\[  \bigcup_{i} g_i = \{1, \dots, p\} \textrm{ and } g_i\cap g_j=\emptyset
\quad\forall i\not=j\]
Brain \textit{networks} consist of one or several brain regions.
The set of brain networks \(\mathcal{H}\) also forms a partition of 
\(\{1, \dots, p\}\) that is consistent with \(\mathcal G\) in
the sense that
\[\forall g\in\mathcal G, h\in\mathcal H,\quad
\textrm{ either } g\subset h\textrm{ or }g\cap h = \emptyset.\]
This allows for an unambiguous assignment of each region \(g\in\mathcal G\) to one
network \(h\in\mathcal H\) and thus generates a tree structure.
A root node is added to contain all voxels.

For a brain image \(w\in\mathbb{R}^p\) and a group \(g\), the vector 
\(w_g\in\mathbb{R}^{|g|}\) is defined as the restriction of \(w\) to the coordinates
 in \(g\). The penalty structured by network
and region information can then be written as
\[\Omega(w) = \alpha\sum_{h\in\mathcal H}\eta_h\|w_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|w_g\|_2.\]
As originally recommended \cite{yuan2006model},
we set \(\eta_g = 1/\sqrt{|g|}\) to
account for discrepancy in group sizes. The hierarchy-level-specific factors 
\(\alpha > 0\) and \(\beta > 0\) can tradeoff region-weighted and
network-weighted models against each other.
Decreasing \(\alpha\) leads to less 
penalization of brain networks and thus the tendency for fully active groups
and dense brain maps. If at the same time \(\beta\) is increased to 
induce group sparsity, then only the structure of brain regions encoded
by \(\mathcal G\) is acknowledged. Conversely, if \(\beta\) is chosen 
sufficiently small and \(\alpha\) increased,
the detected structure will derive from \(\mathcal H\), leading to the
selection of brain networks rather than regions.

@@

The prediction problem at hand is a multiclass classification. We choose to
attack this using one-versus-rest scheme on a binary logistic regression.
The one-versus-rest classification strategy is
chosen to obtain one weight map per class for display and model diagnostics.
Its loss can be written as
\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
if \(y\in\{-1, 1\}\) and with \(x_i\in\mathbb{R}^p\) the training sample brain images.
We optimize parameters \(w\) using an iterative forward-backward
scheme analogous to the FISTA solver for the lasso \cite{beck2009}.

@@

%
\begin{figure*}
\vspace{-0.6cm}
\begin{centering}
% \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
\includegraphics[width=0.60\textwidth]{../figures/ROC_ALL_perclass.png}
\vspace{-0.65cm}
\caption{\textbf{Prediction performance across sparsity priors.}
Comparing the performance of logistic regression estimators
with 6 different structured and unstructered
sparse regularization penalties (\textit{colors})
in classifying neural activity from 18 psychological tasks.
The area under the curve (AUC)
is provided on an identical test set
as class-wise measure (\textit{y-axis}) and across-class mean (\textit{legend}).
%
% \textit{Hierarchical Tree Sparsity}: Structured
% $\ell_1/\ell_2$-block norm with a hierarchy of
% region and network priors
% exhibited the best out-of-sample performance
% ($\alpha = 1, \beta = 1$).
% \textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
% imposed a minimum of relevant brain voxels without
% assuming special structure.
% \textit{Elastic-Net}: Unstructured logistic regression
% with interpolation between $\ell_1$- and $\ell_2$-norm 
% imposed an equilibrium between sparsity and model fit.
% \textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
% norm (with additional $\ell_1$ term)
% imposed region compartments, but naive to network structure.
% \textit{Trace-norm}: Structured trace-norm penalization
% imposed low-rank structure
% with sparsity of unknown ``network'' patterns,
% but naive to region structure.
%
Simultaneous knowledge of both region and network neighborhoods
was hence most beneficial for predicting
tasks from neural activity.
}
\end{centering}
\label{fig_sparsities}
\vspace{-0.6cm}
\end{figure*}
%
% \paragraph{Implementation.}
\subsection{Implementation}
All experiments were performed in Python.
We used \textit{nilearn} to process and resphape
the extensive neuroimaging data 
\cite{abrah14},
\textit{scikit-learn} to design machine-learning
data processing pipelines
\cite{pedr11},
and
\textit{SPAMs} for numerically optimized
implementations of the sparse learners
(\url{http://spams-devel.gforge.inria.fr/}).
All Python scripts that generated the results are
accessible online for reproducibility and reuse
(\url{http://github.com/anonymous/anonymous}).
% (\url{http://github.com/banilo/nips2015}).
\nopagebreak
\subsection{Data}
% \paragraph{Data.}
As the currently biggest open-access dataset in brain imaging,
we chose brain data from the HCP
\cite{barch2013}.
Neuroimaging data with labels of ongoing psychological processes
were drawn from 500
healthy HCP participants.
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants.
% (see appendix for detailed descriptions of dataset and tasks).
% across participants (Table \ref{table_tasks}).
The HCP data incorporated $n$ = 8650 first-level activity maps
from 18 diverse paradigms in a common $60\times72\times60$ space of
3mm isotropic gray-matter voxels.
Hence,
the present analyses were based on task-labeled HCP maps of neural
activity with z-scored $p$ = 79,941 voxels.

@@

Across experiments with stratified and shuffled
cross-validation (90\%/10\% train/test set) across pooled participant data,
hierarchial tree sparsity was most successful
in distinguishing unseen neural activity maps from 18 psychological tasks
(89.7\% multi-class accuracy, mean AUC 94.8 [+/- 9.1 standard deviation]
mean precision 0.87, mean recall 0.92).
It was closely followed by logistic regression
structured by trace-norm regularization
(89.4\%, mean AUC 90.8 [+/- 14.8],
precision 0.86, recall 0.91).
Lasso featured an average performance comparing to the other sparse estimators
(88.6\%, mean AUC 94.3 [+/- 9.3],
precision 0.86, recall 0.90).
Elastic-Net, in turn, featured an
average performance comparing to the other sparse estimators
(88.1\%, mean AUC 94.1 [+/- 10.2],
precision 0.85, recall 0.84).
Introducing a-priori knowledge of brain region compartments
by sparse group sparsity
(87.9\%, mean AUC 93.9 [+/- 10.1], precision 0.85, recall 0.90)
and
by group sparsity
(87.9\%, mean AUC 84.7 [+/- 17.3], precision 0.85, recall 0.90)
performed worst.

>>>>

\begin{abstract}
    Structured sparsity penalization has recently improved
    statistical models applied to high-dimensional data in various domains.
    %
    As an extension to medical imaging,
    the present work incorporates
    priors on network hierarchies of brain regions into
    logistic-regression to distinguish neural activity effects.
    These priors bridge two separately studied levels
    of brain architecture:
    functional segregation into regions and
    functional integration by networks.
    %
    Hierarchical region-network priors are shown to better classify
    and recover 
    18 psychological tasks than other sparse estimators.
    Varying the relative importance of
    region and network structure within the hierarchical tree penalty
    captured complementary aspects of the neural activity patterns.
    %
    Local and global priors of neurobiological knowledge
    are thus demonstrated to offer advantages in
    generalization performance, sample complexity,
    and domain interpretability.
\end{abstract}

\section{Introduction}
% sparsity
Many quantitative scientific domains underwent a
recent shift from the classical ``long data" regime to
the high-dimensional ``wide data" regime.
% the high-dimensional regime (i.e., ``wide data") \cite{jordan2015massive}.
In the brain imaging domain,
many contemporary technologies for acquiring brain signals yield many
more variables per observation than
total observations per data sample.
This $n \ll p$ scenario challenges various statistical methods from
classical statistics.
For instance,
estimating generalized linear models without additional assumptions
yields an underdetermined system of equations.
%
Many such ill-posed estimation problems
have benefited from
\textit{sparsity} assumptions
\cite{bach2012optimization}.
Those act as regularizer by encouraging zero coefficients
in model selection.
Sparse supervised and unsupervised
learning algorithms have proven to yield
statistical relationships that can be readily
estimated, reproduced, and interpreted.
%
Moreover, \textit{structured sparsity} can impose
domain knowledge on the 
statistical estimation,
thus shrinking and selecting variables guided by
expected data distributions
\cite{bach2012optimization}.
These restrictions to model complexity
are an attractive plan of attack
for the $\textgreater$100,000 variables per brain map.
Yet, what neurobiological structure best lends itself
to exploitation using structured sparsity priors?

@@

\section{Methods}
This paper contributes a neuroscience adaptation of hierarchical structured

@@

to create a new class of convex sparse penalty terms.

@@

global integration when discriminating defined psychological tasks

@@

this approach simultaneously infers

@@

\begin{wrapfigure}{r}{0.45\textwidth}
\includegraphics[width=0.45\textwidth]{../figures/level_schematic_crop.pdf}
\vspace{-0.7cm}
  \caption{\textbf{Hierarchical Tree Prior.}
  % Abc
  % \textit{Left:} Def
\label{fig_prior_penalty}
\end{wrapfigure}

Major brain networks emerge in human individuals around birth
\cite{doria2010}.
Their nodes have more
similar functional profiles than nodes from different networks
\cite{anderson2013}.
As a popular method for network extraction,
ICA \cite{beckmann2005} yields continuous brain maps with
voxel-level resolution. The region nodes of ICA
network are spatially disjoint sets of voxel groups that
agree with boundaries of brain atlases.
Hence,
each region from a brain atlas can be uniquely associated with one of
the extracted ICA networks.
%
Here, previously published network definitions
obtained using ICA \cite{smith2009}
and
region definitions obtained from
spatially constrained clustering \cite{crad12}
allowed constructing a hierarchy of global ICA networks with their
assigned local cluster regions
(Figure \ref{fig_priors}).
The ensuing network-region tree was used as a frequentist prior
of expected weight distributions
to advantageously bias supervised model fitting.

Specifically, this tree structure was plugged into
hierarchical sparsity penalty terms
\cite{jenatton2012multi}.
It extends the group lasso
\cite{yuan2006model}
by permitting variable groups that contain each other
in a nested tree structure.
The first hierarchical level are
the network groups with all
the voxels of the brain regions associated with them.
Each network node in turn descends into a second hierarchical level with
brain regions of neighboring voxels
(Figure \ref{fig_prior_penalty}).
%
Induced by the region-network sparsity tree,
a child node enters the set of relevant voxel variables only
if its parent node has been selected
\cite{bach2012optimization}.
Conversely,
if a parent node is deselected,
also the voxel variables of all child nodes are deselected.
%
Moreover,
the coefficients of all region or all network groups can
be weighed individually.
Trading off the voxel penalties of the network level against the
voxel penalties of the region level
we can design distinct estimation regimes.
%
% Setting a low penalty on the network groups makes it is probable
% that all of them are active in the estimated weight maps. If we then select
% higher penalties on region groups, selection of relevant region groups is
% forced without obeying network definitions.
% Conversely, setting low penalties on the region definitions
% makes it possible for
% all voxels to be active. Selecting higher penalties on the networks then
% leads to a selection of networks with all regions associated with it.
%
% This region-network equilibrium allows inspecting the relative contributions
% of the region and network levels
% of the hierarchical tree prior.

% \paragraph{Problem formulation.}
\subsection{Problem formulation}
We formulate our estimation problem in the framework of regularized
empirical risk
minimization applied to linear models.
The goal is to estimate a good predictor of psychological tasks
given a single brain image. Let the set
\(\mathbf{X}\in\mathbb{R}^{n \times p}\) represent brain
images of \(p > 0\) voxels.
We then minimize the risk \(\mathcal L(\hat y, y)\) with
\(\hat y = f(\mathbf{X} \mathbf{\hat w} + \mathbf{\hat b})\), where \(f\) is a link function 
(e.g., sigmoid for logistic regression, identity for linear regression),
and \(\mathcal L\) usually represents an appropriate negative loglikelihood.
We incorporate an informative prior through regularization:
\[ \mathbf{\hat{w}, \hat{b}} = \argmin_{w, b} \mathcal L(f(\mathbf{X}\mathbf{w} + \mathbf{b}), y) + \lambda\Omega(\mathbf{w}),\]
where \(\lambda > 0\) and \(\Omega\) is the regularizer.
Brain \textit{regions} are defined as disjoint groups of voxels. Let \(\mathcal G\)
be a partition of \(\{1, \dots, p\}\), i.e.
\[  \bigcup_{i} g_i = \{1, \dots, p\} \textrm{ and } g_i\cap g_j=\emptyset
\quad\forall i\not=j\]
Brain \textit{networks} consist of one or several brain regions.
The set of brain networks \(\mathcal{H}\) also forms a partition of 
\(\{1, \dots, p\}\) that is consistent with \(\mathcal G\) in
the sense that
\[\forall g\in\mathcal G, h\in\mathcal H,\quad
\textrm{ either } g\subset h\textrm{ or }g\cap h = \emptyset.\]
This allows for an unambiguous assignment of each region \(g\in\mathcal G\) to one
network \(h\in\mathcal H\) and thus generates a tree structure.
A root node is added to contain all voxels.
For a brain image \(\mathbf{w}\in\mathbb{R}^p\) and a group \(g\), the vector 
\(\mathbf{w}_g\in\mathbb{R}^{|g|}\) is defined as the restriction of \(\mathbf{w}\) to the coordinates
 in \(g\). The penalty structured by network
and region information can then be written as
\[\Omega(\mathbf{w}) = \alpha\sum_{h\in\mathcal H}\eta_h\|\mathbf{w}_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|\mathbf{w}_g\|_2.\]
As originally recommended \cite{yuan2006model},
we set \(\eta_g = 1/\sqrt{|g|}\) to
account for discrepancy in group sizes. The hierarchy-level-specific factors 
\(\alpha > 0\) and \(\beta > 0\) can tradeoff region-weighted and
network-weighted models against each other.
Decreasing \(\alpha\) leads to less 
penalization of brain networks and thus the tendency for fully active groups
and dense brain maps. If at the same time \(\beta\) is increased to 
induce group sparsity, then only the structure of brain regions encoded
by \(\mathcal G\) is acknowledged. Conversely, if \(\beta\) is chosen 
sufficiently small and \(\alpha\) increased,
the detected structure will derive from \(\mathcal H\), leading to the
selection of brain networks rather than regions.

@@

The prediction problem at hand is a multiclass classification. We choose to
attack this using one-versus-rest scheme on a binary logistic regression.
The one-versus-rest classification strategy is
chosen to obtain one weight map per class for display and model diagnostics.
Its loss can be written as
\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, \mathbf{w}\rangle)) + \lambda\Omega(\mathbf{w}),\]
if \(y\in\{-1, 1\}\) and with \(x_i\in\mathbb{R}^p\) the training sample brain images.
We optimize parameters \(\mathbf{w}\) using an iterative forward-backward
scheme analogous to the FISTA solver for the lasso \cite{beck2009}.

@@

%
\begin{figure*}
\vspace{-0.6cm}
\begin{centering}
% \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
\includegraphics[width=0.60\textwidth]{../figures/ROC_ALL_perclass.png}
\vspace{-0.65cm}
\caption{\textbf{Prediction performance across sparsity priors.}
Comparing the performance of logistic regression estimators
with 6 different structured and unstructered
sparse regularization penalties (\textit{colors})
in classifying neural activity from 18 psychological tasks.
The area under the curve (AUC)
is provided on an identical test set
as class-wise measure (\textit{y-axis}) and across-class mean (\textit{legend}).
%
% \textit{Hierarchical Tree Sparsity}: Structured
% $\ell_1/\ell_2$-block norm with a hierarchy of
% region and network priors
% exhibited the best out-of-sample performance
% ($\alpha = 1, \beta = 1$).
% \textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
% imposed a minimum of relevant brain voxels without
% assuming special structure.
% \textit{Elastic-Net}: Unstructured logistic regression
% with interpolation between $\ell_1$- and $\ell_2$-norm 
% imposed an equilibrium between sparsity and model fit.
% \textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
% norm (with additional $\ell_1$ term)
% imposed region compartments, but naive to network structure.
% \textit{Trace-norm}: Structured trace-norm penalization
% imposed low-rank structure
% with sparsity of unknown ``network'' patterns,
% but naive to region structure.
%
Simultaneous knowledge of both region and network neighborhoods
was hence most beneficial for predicting
tasks from neural activity.
}
\end{centering}
\label{fig_sparsities}
\vspace{-0.6cm}
\end{figure*}
%
% \paragraph{Implementation.}
\subsection{Implementation}
All experiments were performed in Python.
We used \textit{nilearn} to process and resphape
the extensive neuroimaging data 
\cite{abrah14},
\textit{scikit-learn} to design machine-learning
data processing pipelines
\cite{pedr11},
and
\textit{SPAMs} for numerically optimized
implementations of the sparse learners
(\url{http://spams-devel.gforge.inria.fr/}).
All Python scripts that generated the results are
accessible online for reproducibility and reuse
(\url{http://github.com/anonymous/anonymous}).
% (\url{http://github.com/banilo/nips2015}).
\nopagebreak
\subsection{Data}
% \paragraph{Data.}
As the currently biggest open-access dataset in brain imaging,
we chose brain data from the HCP
\cite{barch2013}.
Neuroimaging data with labels of ongoing psychological processes
were drawn from 500
healthy HCP participants.
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants.
% (see appendix for detailed descriptions of dataset and tasks).
% across participants (Table \ref{table_tasks}).
The HCP data incorporated $n$ = 8650 first-level activity maps
from 18 diverse paradigms in a common $60\times72\times60$ space of
3mm isotropic gray-matter voxels.
Hence,
the present analyses were based on task-labeled HCP maps of neural
activity with $p$ = 79,941 z-scored voxels.

@@

Across experiments with stratified and shuffled
cross-validation (90\%/10\% train/test set) across pooled participant data,
hierarchial tree sparsity was most successful
in distinguishing unseen neural activity maps from 18 psychological tasks
(89.7\% multi-class accuracy, mean AUC 0.948 [+/- 0.091 standard deviation]
mean precision 0.87, mean recall 0.92).
It was closely followed by logistic regression
structured by trace-norm regularization
(89.4\%, mean AUC 0.908 [+/- 0.148],
precision 0.86, recall 0.91).
Lasso featured an average performance comparing to the other sparse estimators
(88.6\%, mean AUC 0.943 [+/- 0.093],
precision 0.86, recall 0.90).
Elastic-Net, in turn, featured an
average performance comparing to the other sparse estimators
(88.1\%, mean AUC 0.941 [+/- 0.102],
precision 0.85, recall 0.84).
Introducing a-priori knowledge of brain region compartments
by sparse group sparsity
(87.9\%, mean AUC 0.939 [+/- 0.101], precision 0.85, recall 0.90)
and
by group sparsity
(87.9\%, mean AUC 0.847 [+/- 0.173], precision 0.85, recall 0.90)
performed worst.
